Re-finding to support a Deep Web Question Answering System

### 2010-03-04 paper/semsearch10/content/abstract.tex
latest version all of jnw & pete 1st changes made

\begin{abstract}
- It is difficult to answer question that change over time
- However, if the method of answering the question can be realized, the question can be easily answered
- We are building a system that supports a learning how to answer particular questions
- We can answer questions that are semantically similar to our store of questions
- We do this by building a semantic library ...
\end{abstract}

>>>>

\begin{abstract}
- It is difficult to answer questions that change over time
- However, if the method of answering the question can be realized, the question can be easily answered
- We are building a system that supports a learning how to answer particular questions
- We can answer questions that are semantically similar to our store of questions
- We do this by building a semantic library ...
\end{abstract}

### 2010-03-04 paper/semsearch10/content/example.tex
latest version all of jnw & pete 1st changes made

The end-user employs the Morpheus question-answering system much like a
search engine with a natural-language interface. One can type a question
in a text box and receive a response from the system. Those questions
dealing with an ontological realm familiar to the system, whose form is
similar to previously answered queries in that realm, and that can be
answered using (possibly deep web) information from a source the system
has encountered can yield relevant responses.

@@

Figure \ref{fig:screenshot} shows a screenshot of a typical Morpheus
interaction. The user has typed a question ``Blah blah blah!!!!!!?'' and
received a response together with information describing assumptions
about the question, the likely relevance of the answer provided,
the source of information, and the method of answer production.

Each answer to a question is created using a \emph{query response
  method} (QRM). A QRM is constructed when a special user, known as a
\emph{guide} answers a question using an instrumented web browser (the
\emph{query response recorder} or QRR) that records web
interactions. The system extracts the relevant artifacts of the
guide's actions and stores them in the QRM. The QRM is characterized
by a \emph{semi-structured query} (SSQ), a schematic representation of
the information contained in the query, namely the inputs and output
contexts---the \emph{who, what, when,} and \emph{where}
categories---that characterize the question together with an
appropriately generalized representation of the guide's browser
interactions.  The \emph{query response evaluator} (QRE) evaluates a
query by binding specific arguments to its input parameters and
replaying the generalized web interactions the guide used to answer
the original question.

>>>>

The end-user employs the Morpheus question-answering system much like a search engine with a natural-language interface. One can type a question in a text box and receive a response from the system. The system uses previously answered queries to answer new questions.  The reused questions have have a similar form, and the same ontological realm, and employ sources that will yield relevant solutions.  We focus our on the sources that are hidden behind web forms, or the \emph{deep web}.

@@

Figure \ref{fig:screenshot} shows a screenshot of a typical Morpheus
interaction. The user has typed a question ``Blah blah blah!!!!!!?'' and
received a response data.  Included with the response is together with information describing assumptions
about the question, the likely relevance of the answer provided,
the source of information, and the method of answer production.

Each answer to a question is created using a \emph{query response
  method} (QRM). A QRM is constructed when a special user, known as a
\emph{guide}, answers a question using an instrumented web browser (the
\emph{query response recorder} or QRR) that records web
interactions. The system extracts the relevant artifacts of the
guide's actions and stores them in the QRM. The QRM is characterized
by a \emph{semi-structured query} (SSQ), a schematic representation of
the information contained in the query, namely the input and output
contexts---the \emph{who, what, when,} and \emph{where}
categories---that characterize the question.  In addition the QRR has categorized an
appropriately generalized representation of the guide's browser
interactions.  The \emph{query response evaluator} (QRE) evaluates a
query by binding specific arguments to its input parameters and
replaying the generalized web interactions the guide used to answer
the original question.
